Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd

#### not take -> fail
```{r SR TPF, eval = FALSE}

#
# SR by hand

# rhs = current course
d_transcript_cum_current <- d_transcript_cum %>%
  unnest(
    course_current,
    .drop = FALSE
    ) %>%
  rename(
    rhs = course_current
    )

# lhs = course not so far
d_transcript_cum_current %>%
  unnest(
    course_not_so_far,
    .drop = FALSE
    ) %>%
  rename(
    lhs = course_not_so_far
    ) %>%
  count(
    lhs, 
    rhs,
    sort = TRUE
    ) %>%
  filter(str_detect(rhs, "fail"))
```

>>>>

#### not take -> fail
```{r SR TPF, eval = FALSE}
#
# SR

x <- d_transcript_cum %>%

  # rhs
  unnest(
    rhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(rhs, "low")
    ) %>%

  # lhs
  unnest(
    lhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(lhs, "not")
    ) %>%

  # support
  count(
    lhs,
    rhs
    )
```
